---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# `{Webglace}`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Installation

You can install the development version of `{Webglace}` like so:

```{r, eval = FALSE}
devtools::install_github("jspowley/Webglace")
```

## Run

Webglace is run in orchestration a noVNC instance and Selenium instance. To run with the supporting applications, navigate to the init folder and run:

```{bash, eval = FALSE}
docker-compose -p webglace up -d
```

This starts a local network in docker running the application with its dependencies.

To end a session, run:

```{bash, eval = FALSE}
docker-compose -p webglace down
```

For live testing, branch development, and running shiny from RStudio, follow the above procedure from the init/compose_live_testing folder. The docker-compose file at this directory only runs the application dependencies. From here you are free to run the Webglace separately from R in terminal or RStudio.

You can launch the application by running:

```{r, eval = FALSE}
Webglace::run_app()
```

Or when developing branches, by using the following when working in an RProjects workflow:

```{r, eval = FALSE}
golem::run_dev()
```

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

Here are the tests results and package coverage:

```{r, error = TRUE}
devtools::check(quiet = TRUE)
```

```{r echo = FALSE}
unloadNamespace("Webglace")
```

```{r, error = TRUE}
covr::package_coverage()
```
